# Keto No-Fry Buffalo Cauliflower {#intro}

Ever had the incredible Buffalo Cauliflower from Erewhon? If you haven’t, you MUST! They are probably the first thing that is sold out everytime we shop...THEREFORE I decided to make our own...without the deep fryer! They also use rice flour (which is da bomb) but for a more keto friendly recipe simply replace with almond flour ;)

So here you have it- a simple guide to making Vegan, Gluten-free, Keto, No-Fry Buffalo Cauliflower. Pals and I just so happen to love these on a rainy days here in LA! 

_This way to yum…_

__**Time**__: 35 Mins. __**Yields**__: Roughly two cups

```{r, include=FALSE}
#You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

#Figures and tables with captions will be placed in `figure` and `table` environments, respectively.
```

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
